Scheduling and Vectorization for MPC

### 2022-03-16 paper_SIMD.tex
Minor edits to paper?
Add initial semantic analysis description

@@

Linearization is the concretization operation, which, as we mentioned earlier computes a schedule.
The concretization function $\gamma: A \rightarrow C$ is defined as an interpretation of
MPC Source syntax, as it is standard. The concretization of each one 
of the base statements is as follows: 
\[\begin{array}{l}
\gamma(\x[i,J,k] = \mathit{op\_SIMD}(\y[i,J,k], \z[i,J,k])) = \\ 
\x[i,0,k] = \y[i,0,k] \; \mathit{op} \; \z[i,0,k] \;\; || \\
\x[i,1,k] = \y[i,1,k] \; \mathit{op} \; \z[i,1,k] \;\; || \; ...\; || \\
\x[i,I-1,k] = \y[i,I-1,k] \; \mathit{op} \; \z[i,I-1,k]
\end{array}\]
meaning that the vectorized dimension(s) are expanded into parallel statements. || introduces SIMD (parallel) execution.

The concretization of the FOR statement is as follows:
\[ \gamma(\texttt{FOR} \; 0 \le i < I: s) = \gamma(s)[0/i] ; \gamma(s)[1/i] ; ... \gamma(s)[I-1/i] \]
$\gamma$ simply unrolls the loop substituting $i$ with 0, 1, etc. Here ; denotes sequential execution.

>>>>

Our compiler performs the following semantic analysis steps:

\begin{enumerate}
  \item
        \textbf{Parsing}:
        Use Python's \texttt{ast} module to parse the input source code to a Python AST.
  \item
        \textbf{Syntax checking}:
        Ensure that the AST matches a restricted subset that our compiler supports.
        This step outputs an instance of the \texttt{restricted\_ast.Function} class, which represents our restricted subset of the Python AST.
  \item
        \textbf{3-address CFG conversion}: TODO
  \item
        \textbf{SSA conversion}:
        Convert the 3-address CFG to SSA with Cytron's algorithm.
\end{enumerate}

@@

Linearization is the concretization operation, which, as we mentioned earlier computes a schedule.
The concretization function $\gamma: A \rightarrow C$ is defined as an interpretation of
MPC Source syntax, as it is standard. The concretization of each one 
of the base statements is as follows: 
\[\begin{array}{l}
\gamma(\x[i,J,k] = \mathit{op\_SIMD}(\y[i,J,k], \z[i,J,k])) = \\ 
~~\x[i,0,k] = \y[i,0,k] \; \mathit{op} \; \z[i,0,k] \;\; || \\
~~~~\x[i,1,k] = \y[i,1,k] \; \mathit{op} \; \z[i,1,k] \;\; || \; ...\; || \\
~~~~~~\x[i,I-1,k] = \y[i,I-1,k] \; \mathit{op} \; \z[i,I-1,k]
\end{array}\]
meaning that the vectorized dimension(s) are expanded into parallel statements. || introduces SIMD (parallel) execution.

The concretization of the FOR statement is as follows:
\[ \gamma(\texttt{FOR} \; 0 \le i < I: s) = \gamma(s)[0/i] \; ; \; \gamma(s)[1/i] \; ; \; ... \gamma(s)[I-1/i] \]
$\gamma$ simply unrolls the loop substituting $i$ with 0, 1, etc. Here ; denotes sequential execution.
